Draft-Theory

### 2024-10-31 drafttheory.Rmd
theoryfirstdraftpush

```{=html}
<!-- -->
```
-   Hypothesis 2: between the collaboration networks of both departments (pol. sci & soc.) scholars in the sociology department prefer to collaborate with same-sex scholars less strongly than scholars from the pol. sci. department

@@

RQ2 b? Do we observe gender homophily (preferences) in collaboration networks...

Questions:

-   Does this question need to ask whether we observe gender homophily in collaboration networks to begin with?

    -   Isn't that the same question as RQ1a then?

    -   *yes and no. ;-) this is your hypothesis for your RSiena models. whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).\
        I hope that you understand that this **dyadic preferences does not necessarily translates to your macro-outcome** (because of all structural effects possibly at play and other covariate-effects).*

Hypothesis 3:

RQ3: How to does gender homophily affect collaboration differently for collaborations between staff who have published in low vs. high prestige journals?

aka. looking at whole sample: does the gender homophily in collaboration networks look different depending on the scholars' publishing prestige?

*Try to **reformulate this to your RSiena model** and not at your macro-level. I let you struggle a little bit on this last one okay.\
But the idea is fine; whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*

>>>>

-   (logical error: yeah but that only makes sense if men are the only ones initiating and breaking ties, right?)

```{=html}
<!-- -->
```
-   **Hypothesis 2**: between the collaboration networks of both departments (pol. sci & soc.) scholars in the sociology department prefer to collaborate with same-sex scholars less strongly than scholars from the pol. sci. department

@@

```{=html}
<!-- -->
```
-   *hypothesis for your RSiena models: whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).*

    -   **confusion: where would the comparison between depatments be here? this wold fit rq one more, but that one is supposed to be on the network level but this is about dyads...**

-

```{=html}
<!-- -->
```
-   **Hypothesis 3:** On the ego level, the preference of *men to work with men and women with women, (controlled for structural network effects), is less influential in the choice to collaborate if the alter is someone who published in a high-prestige journal.*

    -   [RQ3: How to does gender homophily affect collaboration differently for collaborations between staff who have published in low vs. high prestige journals? ego-level] *idea: whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*
